### 2021-02-09 final_report/include/CAMT.tex
added part about depconfigs

@@

\subsection{Grammar generation} \label{grgn}
The result of this UD-to-GF conversion is still a series of tree alignments, but their resulting format makes a substantial difference, since GF ASTs can be used to obtain the rules of a generative grammar. \texttt{gf-ud} also provides a way to do this, given an \textit{extraction grammar} and a \textit{morphological dictionaries} of the languages of the alignments. \smallskip

>>>>

Conversion is based on annotations defining the relation between UD trees and GF ASTs, which we refer to as \textit{dependency configurations}. 
While going into all the notational details is beyond the scope of this project\footnote{a comprehensive description of \texttt{gf-ud}'s annotation scheme is available at \url{github.com/GrammaticalFramework/gf-ud/blob/master/doc/annotations.md}.}, an example of one such configuration is

\begin{verbatim}
    #fun PredVP	nsubj head
\end{verbatim}

which specifies that a \texttt{PredVP} (predicative Verb Phrase), defined in the RGL as a function of type

\begin{verbatim}
    PredVP : NP -> VP -> Cl
\end{verbatim}

i.e. a function taking two arguments, an \texttt{NP} (Noun Phrase) and a \texttt{VP} (Verb Phrase) and returning a \texttt{Cl} (clause), corresponds to a UD tree whose head, the VP, has a \texttt{nsubj} attached to it. Appendix \ref{c} lists the dependency configurations used for UD-to-GF conversion in the context of this project.
\smallskip

@@

\subsection{Grammar generation} \label{grgn}
The result of this UD-to-GF conversion is still a series of tree alignments, but their resulting format makes a substantial difference, since GF ASTs can be used to obtain the rules of a generative grammar. \texttt{gf-ud} also provides a way to do this, given an \textit{extraction grammar} and a \textit{morphological dictionary} of the languages of the alignments. \smallskip
